### 2017-04-13 paper1.tex

\chapter{A method to correct upwelling longwave radiation to estimate hemispherical urban surface temperature}\label{paper1}

@@

Within urban climatology, a combination of satellite, aerial, and ground-based thermal remote sensors have been integral in elucidating the spatial \cite{Roth1989}, temporal \cite{Peng2012}, and geometric \cite{Voogt1997} effects of the built environment on land T\textsubscript{surf}; in evaluating and partitioning urban surface energy balances \cite{BastiaanssenW.G.M.1998, Yamaguchi2005} and; in characterizations of the relationship between surface and \gls{blayer} air temperatures (T\textsubscript{air}) \cite{Stoll1992}. These advances have been aided by substantial improvements in sensor spatial, spectral, and radiometric resolutions, and by the proliferation of both large-scale public satellite remote sensing campaigns and low-cost aerial and near-ground thermography. However, in spite of it's widespread usage, several questions concerning the use and validity of urban remote thermal remote sensing, first posed in Roth et al. 1989 \cite{Roth1989}, have yet to be sufficiently answered, viz,

>>>>

\chapter{A hemispherical atmospheric correction method to derive time-continuous urban surface temperature}\label{paper1}

@@

Within urban climatology, a combination of satellite, aerial, and ground-based thermal remote sensors have been integral in elucidating the spatial \cite{Roth1989}, temporal \cite{Peng2012}, and geometric \cite{Voogt1997} effects of the built environment on land T\textsubscript{surf}; in evaluating and partitioning urban surface energy balances \cite{BastiaanssenW.G.M.1998, Yamaguchi2005} and; in characterizations of the relationship between surface and \gls{blayer} air temperatures (T\textsubscript{air}) \cite{Stoll1992}. These advances have been aided by substantial improvements in sensor spatial, spectral, and radiometric resolutions, and by the proliferation of both large-scale public satellite remote sensing campaigns and low-cost aerial and near-ground thermography. However, in spite of it's widespread usage, several questions concerning the use and validity of urban remote thermal remote sensing, first posed in Roth et al. 1989 \citet{Roth1989}, have yet to be sufficiently answered, viz,
